\chapter*{Acknowledgements}
\thispagestyle{empty}

% Thank:
% - supervisor, co
First and foremost I would like to express my deepest gratitude to my advisor and co-advisor, Prof. Multerer and Dr. Baroli for their invaluable feedback, continuous support and patience during my Master's Thesis. Furthermore, I thank them for having given me the opportunity to collaborate through this thesis work.
\\
% - master director
I could not have undertaken this journey without my Master directors Prof. Schenk and Prof. Wit. I am extremely grateful for their guidance, mentorship and advice throughout my Master studies.
\\
% - professors of faculty
% From Polya How to solve it
% forster independent thinking  by challenging curiosity, stimulating questions and delving into the motives behind theory.
% tutti i professori che ho avuto, shaped my interest, saziato sete curiosità
I would like to extend my deepest appreciation to all professors I had during my studies at Usi. Their stimulating questions and push to enquire motives behind theory challenged my curiosity, shaped my interests and fostered my independent thinking.
\\
% - research group 
% discussions, suggestions
% listening the challenges I faced and insightful suggestions
I also had great pleasure of discussing with the research group of Prof. Multerer the challenges I faced during this thesis work. I thank them for their affability  and insightful suggestions.
\\
% - classmates
% friends I made along the way
% mutual support and good times we had together
% be it during a group revision session before an exam of during light hearted moments.
Special thanks to my cohort members and to the friends I made along the way. I will never forget the good times we had together.
\clearpage